Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-20 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Fix naming of zscore to test_statistic

```{r, wkspace-setup}
# project directory & data/results folders
setwd("/n/irizarryfs01_backed_up/kkorthauer/FDR")
datdir <- "/n/irizarryfs01_backed_up/kkorthauer/FDR/DATA/GWAS/"
resdir <- "/n/irizarryfs01_backed_up/kkorthauer/FDR/RESULTS/GWAS/"

@@

Before moving on, we'll rename the relevant columns so that they will use common terms
across the different datasets. We'll also add a 'zscore' column, and subset on a 
toy example before moving on to the full dataset.

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(zscore = effect_size/SE)

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:10000,]
```

@@

```{r, GWAS1-plot, results="hide"}
#

>>>>

```{r, wkspace-setup, results='hide', message=FALSE, warning=FALSE}
# project directory & data/results folders
setwd("/n/irizarryfs01_backed_up/kkorthauer/FDR")
datdir <- "/n/irizarryfs01_backed_up/kkorthauer/FDR/DATA/GWAS/"
resdir <- "/n/irizarryfs01_backed_up/kkorthauer/FDR/RESULTS/GWAS/"

@@

Before moving on, we'll rename the relevant columns so that they will use common terms
across the different datasets. We'll also add a 'test_statistic' column, and subset on a 
toy example before moving on to the full dataset.

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(test_statistic = effect_size/SE)

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:50000,]
```

@@

```{r, GWAS1-plot, results="hide", width=15, height=12}
# plot adjusted p-values by effect_size (diagnostic from ASH paper)
plotsim_single(data.frame(assay(sb)), bmi, strat = "effect_size")
